%-------------------------
% Resume in LaTeX
% Template by Sourabh Bajaj (MIT)
% Content: Saahil Parikh
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\publication}[1]{%
  \item\small #1\vspace{-2pt}%
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://saahil.io}{\Large Saahil Parikh}} & \href{https://saahil.io}{saahil.io} \\
  Software Engineer & \href{https://www.linkedin.com/in/saahilparikh}{linkedin.com/in/saahilparikh} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon Web Services}{Seattle, WA}
      {Software Development Engineer 2 -- Elastic MapReduce}{2022 -- Present}
      \resumeItemListStart
        \resumeItem{Distributed systems}
          {Design and operate multiple microservices spanning EMR cluster orchestration, inter-node communication, resilience, and recovery across a high-scale distributed fleet.}
        \resumeItem{LLM ecosystem}
          {Maintain a prompt-optimization library, author an MCP (Model Context Protocol) server, and ship vector-database integrations across the LLM stack.}
        \resumeItem{Diagnostics tooling}
          {Mentored an intern to build a node-state diagnostics tool, materially reducing time-to-mitigation on customer escalations.}
        \resumeItem{Disk-pressure resilience}
          {Designed a heuristic disk-management policy that preserves customer data integrity during node instability under high disk pressure.}
        \resumeItem{Cluster start latency}
          {Drove cross-team efforts to investigate and improve key business metrics, including cluster-start latency.}
        \resumeItem{Release process}
          {Established the team's patch-testing and release documentation process, raising production deploy quality.}
        \resumeItem{Configuration}
          {Extracted on-cluster configuration into dedicated files, improving operational flexibility across the service.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Web Services}{Seattle, WA}
      {Software Development Engineer Intern -- Elastic MapReduce}{2021}
      \resumeItemListStart
        \resumeItem{Finite-state-machine analysis}
          {Extended an internal FSM analysis tool for cluster behavior; cut day-long analysis runs to \textasciitilde 16 seconds end-to-end.}
      \resumeItemListEnd

    \resumeSubheading
      {The Boeing Company}{Los Angeles, CA}
      {Software Developer Intern -- Ground Systems \& Satellites}{2018}
      \resumeItemListStart
        \resumeItem{Satellite simulation}
          {Built proprietary satellite simulation software; wrote the communication interface and packet decryption algorithm.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------SELECTED PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeItem{Choose Your Own Adventure}
      {AI-powered text adventure with turn-by-turn narrative, scene art, and voice generation. LangGraph, Amazon Bedrock (Claude, Nova Canvas), Polly; Stripe-billed. \href{https://choose-your-own-adventure.com}{choose-your-own-adventure.com}}
    \resumeItem{Distributed Protocol Visualizer}
      {Interactive Raft visualizer with seeded, deterministic browser simulation; log replication, commit rules, term handling, scrubbable playback. \href{https://github.com/SaahilParikh/distributed-protocol-visualizer}{github.com/SaahilParikh/distributed-protocol-visualizer}}
  \resumeSubHeadingListEnd


%-----------RESEARCH-----------------
\section{Research}
  \resumeSubHeadingListStart
    \publication{Saahil Parikh, Yi Wang. ``\textit{Dynamic Decentralized Line-of-Sight Rapidly-Exploring Random Trees for Multi-Agent Safety Planning}.'' UC Berkeley, 2022.}
    \publication{Saahil Parikh, Jason Li. ``\textit{Bluetooth Low Energy Controlled Quadcopter on the nRF52 Embedded Board}.'' UC Berkeley EECS149, 2021.}
    \publication{Saahil Parikh. ``\textit{Using Artificial Intelligence to Determine the Veracity of News Outlets}.'' 2019.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, CA}
      {B.S.\ Computer Science $\cdot$ B.S.\ Electrical Engineering -- Regents' Scholar}{2019 -- 2022}
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {M.S.\ Computer Science -- Computing Systems specialization}{2023 -- 2026 (Expected)}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
